### 2020-03-03 manuscript/figures.Rmd
add granularity column to table 1

```{r 01_predictors, results='asis', warning=FALSE, echo = FALSE}
knitr::kable('\\includegraphics[width=5in]{"../tables/01_predictors"}', col.names = NULL, caption = "Medians followed by first and third quantiles of predictor variables for 928 lakes.")
```

>>>>

```{r 01_predictors, results='asis', warning=FALSE, echo = FALSE}
knitr::kable('\\includegraphics[width=5in]{"../tables/01_predictors"}', col.names = NULL, caption = "Medians followed by first and third quantiles of predictor variables for 928 lakes. Also shown is whether each predictor is defined as an aggregate or granular measure of agriculture.")
```

### 2020-03-03 tables/01_predictors.Rmd
add granularity column to table 1

dt <- mutate(dt, pretty = case_when(
  nchar(units) > 0 ~ paste0(pretty, " (", units, ")"),
  TRUE ~ pretty), 
  IQR = paste0(q25, " - ", q75))
dt <- dplyr::select(dt, Variable = pretty, 
                    Median = q50, Q25 = q25, Q75 = q75)

knitr::kable(dt, digits = 0, format = "markdown") 
#%>%
 # add_header_above(c(" ", " ", Ranges = 3, " ", " "))
```

>>>>

dt <- mutate(dt, pretty = case_when(
  nchar(units) > 0 ~ paste0(pretty, " (", units, ")"),
  TRUE ~ pretty), 
  IQR = paste0(q25, " - ", q75))
dt <- dplyr::select(dt, Variable = pretty, Granularity = granularity,
                    Median = q50, Q25 = q25, Q75 = q75, category) 
dt <- dt %>%
  mutate(Granularity = factor(Granularity, levels = c("Other", "Granular", "Aggregate")), 
         category = factor(category, levels = c("Land-use cover", "Buffer configuration", "Nutrient inputs", "Nutrient transport", "Lake"))) %>%
  arrange(desc(Granularity), category) %>%
  dplyr::select(-category)

unfill_vec <- function(x) {
  # https://github.com/tidyverse/tidyr/issues/250#issuecomment-344984802
  same <- x == dplyr::lag(x)
  ifelse(!is.na(same) & same, NA, x)
}
dt$Granularity <- unfill_vec(as.character(dt$Granularity))

options(knitr.kable.NA = " - ")
knitr::kable(dt, digits = 0, format = "markdown") 
#%>%
 # add_header_above(c(" ", " ", Ranges = 3, " ", " "))
```
